---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rorqual.morpho

<!-- badges: start -->
<!-- badges: end -->

## Overview

rorqual.morpho is an implementation of the allometric equations in Kahane-Rapport and Goldbogen (2018), allowing users to predict morphological parameters of rorquals from body length measurements.

## Installation

You can install rorqual.morpho from [GitHub](https://github.com/FlukeAndFeather/rorqual.morpho) with:

``` r
# install.packages("devtools")
devtools::install_github("FlukeAndFeather/rorqual.morpho")
```

Note: uncomment and run the first line if you don't have devtools installed.

## Usage

You can use the rorq_\*() family of functions to predict morphological parameters.
Note: rorq_\*() functions will return *Balaenoptera acutorostrata* (species code ba) parameters for *B. bonaerensis* (species code bb).

```{r example}
library(rorqual.morpho)
# Predict the body mass and engulfment capacities of three blue whales of different sizes.
rorq_mass(c("bw", "bw", "bw"), c(18, 20, 22))
rorq_engulf(c("bw", "bw", "bw"), c(18, 20, 22))

# Use dplyr to predict fluke and flipper lengths for a tibble of humpback and minke whales
library(dplyr)
tribble(
  ~ species, ~ length,
  "mn",      8,
  "mn",      11.5,
  "mn",      15,
  "ba",      4.5,
  "ba",      6.75,
  "bb",      9
) %>% 
  mutate(fluke = rorq_fluke(species, length),
         flipper = rorq_flipper(species, length))
```
